The dictionary for characters of smooth group schemes

### 2016-05-21 followup.tex
Getting ready to talk.

In order to provide further justification for referring to objects in $\CCS(G)$ as commutative character sheaves, suppose for the moment that $G$ is a connected, reductive algebraic group over $\Fq$.
In this case, it can be shown that there is a forgetful functor taking every object in $\CCS(G)$ to a Frobenius-stable character sheaf on $G$, in the sense of \cite{lusztig:85a}*{Def.~2.10}, for which the characteristic function is a character of $G(k)$.
Of course, such sheaves represent a small part of Lusztig's geometrization of characters of representations of connected, reductive groups over finite fields,
but they are precisely the part needed to describe characters of such groups.
\bigskip

>>>>

In order to provide further justification for referring to objects in $\CCS(G)$ as commutative character sheaves, suppose for the moment that $G$ is a connected, reductive algebraic group over $\Fq$.
In this case, it can be shown that there is a forgetful functor taking every object in $\CCS(G)$ to a Frobenius-stable character sheaf on $G$, in the sense of \cite{lusztig:85a}*{Def.~2.10}.
Of course, such sheaves represent a small part of Lusztig's geometrization of characters of representations of connected, reductive groups over finite fields,
but they are precisely the part needed to describe characters of such groups.
\bigskip
